IMF and Benchmark Forecasts

### 2024-04-17 manuscript/manuscript.Rmd
update processing according to new benchmark format

bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
  data.table::copy() |>
  .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
  .d(,model := "bvar_qu") |>
  setnames("model", "source") |>
  .d(,error_method := "directional") |>
  .d(,method := "rolling window") #change later

@@

bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
  setnames("model", "source", skip_absent = TRUE) |>
  .d(, source := "bvar_qu") |>
  .d(, method := "rolling window") |>
  .d(, error_method := "absolute")

>>>>

bvar_wis_scores <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
  data.table::copy() |>
  .d(, .(model, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
  .d(,model := ifelse(model == "bvar_qu", "bvar_qu", "bvar_ciss")) |>
  setnames("model", "source") |>
  .d(,error_method := "directional") |>
  .d(,method := "rolling window") #change later

@@

bvar_scores_cvgshort <- fread(here("scores", "bvar_ci_scores_avgcnt.csv")) |>
  setnames("model", "source", skip_absent = TRUE) |>
  .d(, source := ifelse(source == "bvar_qu", "bvar_qu", "bvar_ciss")) |>
  .d(, method := "rolling window") |>
  .d(, error_method := "absolute")
